---
title: "Lab 7 - Multiple linear regression"
author: "Karina Johnston"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(broom)
library(GGally)
library(modelsummary)
```

Exploring the penguins dataset

## Intro to ggpairs

Use the `GGally::ggpairs()` function to create a pairs plot.

```{r}
ggpairs(penguins)
```

Can select groups of columns using the colon

```{r}
# to create a group of graphs for all the selected variables
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species)) +
  theme_classic()

# really important to look at your data to know what variables need to be included
ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  theme_classic() +
  geom_smooth(method = "lm")
```

### Multiple linear regression - penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass). 

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# return just the coefficients:
penguin_lm
```

How would you interpret coefficient for flipper length?

If all other factors were constant, on average for every 1 mm increase in flipper length, the body mass would increase by 51.54g. 

ALWAYS USE IN-LINE CODE REFERENCING - DONT HAND TYPE NUMBERS INTO REPORT.

Use `summary()` function to get more information:

```{r}
summary(penguin_lm)
```

p-value alone should not be grounds for removing or adding a variable from the model
final p-value says the model is doing better (significantly) than random chance

information presented on model fit. for multiple linear regression, use adjusted R-squared value, because more variables usually will raise the R-squared artificially

What does Adj R-sq mean?

The model explains 75.96% of the variance for the penguin body weight. (remember not good or bad, just an explanation of the variance) 

### Use `broom()` functions tidy and glance for more info

Use `broom::tidy()` to get the coefficient summary in a data frame.
Use `broom::glance()` to get the model summary in a data frame.

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

Try using in-line code to refer to bill depth coefficient.

USE IN-LINE CODE TO REFERENCE:
The penguin bill depth coefficient is `r round(penguin_lm_tidy$estimate[3], 2)` 


```{r}
penguin_lm_glance <- glance(penguin_lm)
penguin_lm_glance
```

In-line code to output adjusted R-squared:
`r round(penguin_lm_glance$adj.r.squared, 3)`

## Try another model

We have thought really hard, done a literature review, consulted with experts, deeply explored data, and decided that the three most critical variables to include in this model are (with body mass as the dependent variable):

- flipper length
- species
- sex

Task: create a multiple linear regression model using those three variables
Then take a look at the model outputs and interpret the coefficients

```{r}
penguin_lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

summary(penguin_lm2)
```

Output means that reference level for species is Adelie and sex is female. 

Check out lab6 for equatiomatic to get the equation output.

**HOW TO INTERPRET:**
If everything else is constant, on average for every Chinstrap penguin, we expect the body mass to be 87.6 g smaller than an Adelie penguin. 

If everything else is constant, on average male penguins are 530.4 g more than a female penguin.

body mass of male adelie penguin, 200 mm flippers = 
mass(g) = -365.82 + 20.02(200) + 530.38(1)

### Use `broom::augment()` to see predicted values

```{r}
augment(penguin_lm2)

```



